---
title: "Alcohol vs Seat choice"
author: "Jeanette Serrano"
date: "Sept 23,2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require (knitr)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
people in the back are drinking more        
   
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=davisdata)
```


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))

```

## Conclusions
Based on the charts above, the back row is drinking nearly 10 times the amount of drinks compared to the front row and approximately 3 times as many drinks than the middle row. Based on the inferential graphs, we can conclude that the Middle and Front row have a relationship consisting of nearly the same results and the Back row shares no relationship with any of the other results.  


